Instruction

### 2019-01-24 script/Rmd/instruction.Rmd
Update instrution 24/01

---
title: "Instruction"
author: "Atsuko Tominaga"
date: "18/01/2019"
output:
  html_document:
    css: style.css
---

@@

1. Go to Desktop >> Max alias >> open the "mainPatch.maxpat", the “practicePatch.maxpat” and the “imageDisplay.maxpat”.
2. Move the window of the “imageDisplay.maxpat” to the right (on the screen in front of the piano”) and press F for a fullscreen mode.
3. Read the instruction on the “mainPatch.maxpat" and the "practicePatch.maxpat". <span>**Both patchers cannot be opened at the same time.**</span>
4. Press the "Metro" button on the "blue patcher"practicePatcher" to make sure the sound of a metronome comes from the headphone, not from the computer speaker. <span>**Please do not skip this procedurea otherwise sometimes the metronome does not work properly only for the first time.** # added on 18/01/19</span>
5. Also check whether the piano sounds come from the headphone and MIDI inputs are correctly responded (Pitch and Velocity should change according to key presses on MIDIRecording subpatchers).
6. If the sound of the metronome and the piano does not come from the computer speaker, go to System Preference >> Sound >> Output >> select “Scarllet 6i6 USB”.
7. If you cannot still solve the problem above, please quit Max and relaunch it again. <span># added on 18/01/19</span>
8. Click the “inst_1” button to show a general instruction on the “imageDisplay.maxpat”.
9. Enter SubNr for the current participant.

@@

@@

@@

## Memo for patchers (20/01/19 Updated)
- Change variable names for data storage on practice sub-patchers (data / data_p)

>>>>

---
title: "Instruction"
author: "Atsuko Tominaga"
date: "24/01/2019"
output:
  html_document:
    css: style.css
---

@@

1. Go to Desktop >> Max alias >> open the "mainPatch.maxpat", the “practicePatch.maxpat” and the “imageDisplay.maxpat”.
2. Move the window of the “imageDisplay.maxpat” to the right (on the screen in front of the piano”) and press F for a fullscreen mode.
3. Read the instruction on the “mainPatch.maxpat" and the "practicePatch.maxpat". <span>**Both patchers cannot be opened at the same time.**</span>
4. Press the "Metro" button on the "blue patcher"practicePatcher" to make sure the sound of a metronome comes from the headphone, not from the computer speaker. <span>~~**Please do not skip this procedurea otherwise sometimes the metronome does not work properly only for the first time.** # added on 18/01/19~~</span>
5. Also check whether the piano sounds come from the headphone and MIDI inputs are correctly responded (Pitch and Velocity should change according to key presses on MIDIRecording subpatchers).
6. If the sound of the metronome and the piano does not come from the computer speaker, go to System Preference >> Sound >> Output >> select “Scarllet 6i6 USB”.
7. If you cannot still solve the problem above, please quit Max and relaunch it again. <span># added on 18/01/19</span>
8. Click the “inst_1” button to show a general instruction on the “imageDisplay.maxpat”.
9. Enter SubNr for the current participant.

### Practice Patch <span># added on 24/01/19</span>
![](./image/praPatch.png)

### Main Patch <span># added on 24/01/19</span>
![](./image/mainPatch.png)

### Experimental Design <span># added on 24/01/19</span>
|Condition 1 (teaching / performing)|
|-----------------------------------|
|1st Stimulus (articulation / dynamics) - Block 1|
|2nd Stimulus (dynamics / articulation) - Block 2|

|Condition 2 (performing / teaching)|
|-----------------------------------|
|1st Stimulus (articulation / dynamics) - Block 3|
|2nd Stimulus (dynamics / articulation) - Block 4|

* The order of the conditions is counterbalanced across participants.
* The order of the stimuli is counterbalanced across participants, but it is fixed within one condition (e.g., if a participant start with articulation and move on dynamics in the first condition, he/she will perform in the same order.)

@@

**[ Close practicePatch ]**

**[ Open mainPatch ]**

@@

**[ Explain the musical notation ]**

@@

## Memo for patchers (24/01/19 Updated)
- Change variable names for data storage on practice sub-patchers (data / data_p) <span># added on 20/01/19</span>
- Add a tone counter to detect error (if the number of tones is not equal to 150 after performing, there will be an error in performance) <span># added on 24/01/19</span>
